Supplemental Information:\\ Harnessing Design Principles from Glass Sponges for Structurally Robust Lattice Structures

### 2018-09-17 Supplemental-FernandesWeaverBertoldi_AdvMaterials_2018.tex
.

\section{Designs Considered}
In this study, we focus on four different lattice configurations constrained to deform in an in-plane setting only. In an effort to provide a fair performance compassion between the different designs all of the respective lattice configurations, the total amount of material (i.e. volume or mass) is conserved. Moreover,  we consider a fixed volume ratio between non-diagonal and diagonal elements (chosen to match the sponge geometry) and two different shapes for the cross section of all lattice members: circular and rectangular.  For circular cross-sections  we stay consistent with the geometry found within the biological species. However, since slender members with circular cross section easily buckle out-of-plane when the structure is subjected to compression we must mitigate the issue by pursuing a plane-strain structure such that it's depth slenderness ratio is sufficiently deep to avoid out-of-plane buckling. In order to address this, we converted the biological observations of the cylindrical cross-section into a polygonal section. For this new cross-section type, we assume the structure to be sufficiently deep in plane in comparison the structural length scale (plane strain assumption) to avoid out of plane deformation. The out-of-plane slenderness is scaled accordingly with mass to maintain the depth across all elements constant. A parametric simulation on depth was analyzed to determine the minimum cross-section depth required to prevent out-of-plane buckling. Once the overall minimum depth for all geometries was chosen a factor of safety of 1.5 was added for the finial depth. The approach for minimum out-of-plane depth was further verified experimentally and the value was determined sufficient.

For this new cross-section type, we assume the structure to be sufficiently deep in plane in comparison the structural length scale (plane strain assumption) to avoid out of plane behavior. The cross-section is scaled accordingly with mass while maintaining the depth across all elements constant. In the subsequent sections, we describe in detail the unit cells for the four different designs (Designs A-D).

>>>>

\section{Designs Considered}
In this study, we focus on four different lattice configurations constrained to deform in an in-plane setting only. In an effort to conduct a fair performance comparison between the different designs0, the total amount of material (i.e. volume or mass) is conserved. Moreover,  we consider a fixed volume ratio between non-diagonal and diagonal elements (chosen to match the sponge geometry) and two different shapes for the cross section of all lattice members: circular and rectangular.  For circular cross-sections  we stay consistent with the geometry found within the biological species. However, since slender members with circular cross section easily buckle out-of-plane when the structure is subjected to compression we must mitigate the issue by pursuing a plane-strain structure such that it's depth slenderness ratio is sufficiently deep to avoid out-of-plane buckling. In order to address this, we converted the biological observations of the cylindrical cross-section into a polygonal section. For this new cross-section type, we assume the structure to be sufficiently deep in-plane in comparison the structural length scale (plane strain assumption) to avoid out-of-plane deformation. The cross-section is scaled accordingly with mass while maintaining the depth across all elements constant. The out-of-plane slenderness is scaled accordingly with mass to maintain the depth across all elements constant. A parametric simulation on depth was analyzed to determine the minimum cross-section depth required to prevent out-of-plane buckling. Once the overall minimum depth for all geometries was chosen a factor of safety of 1.5 was added for the finial depth. The approach for minimum out-of-plane depth was further verified experimentally and the value was determined sufficient.

In the subsequent sections, we describe in detail the unit cells for the four different designs (Designs A-D).
